Towards a Machine Learning approach for Aggregate Computing

### 2021-11-28 paper-2021-woa-ac-ml.tex
Shorter org summary

The paper is divided as follow, in \Cref{background} we describe
 the AC framework, showing the context in which
 is typically applied and the overall idea of how it works, and then the motivation of injecting Reinforcement Learning in this paradigm,
 %in \Cref{aggregate-and-machine-learning} we detail the relevant properties of Aggregate Computing in terms of machine learning problems, 
 in \Cref{aggregate-and-rl} we describe a combination of AC with RL and then in
 \Cref{evaluation} we practically applied it in a paradigmatic AC case study,
 finally, \Cref{conclusion} we discuss the result showed and we underline a path toward an in-depth AC and RL integration.

>>>>

The paper is organised as follows. 
%
In \Cref{background} we describe
 the AC framework, %showing the context in which is typically applied and the overall idea of how it works, and then the motivation of injecting Reinforcement Learning in this paradigm,
 and motivate our proposal to inject RL into this paradigm. 
 %in \Cref{aggregate-and-machine-learning} we detail the relevant properties of Aggregate Computing in terms of machine learning problems, 
 In \Cref{aggregate-and-rl}, we describe the details of our integration of AC with RL.
Then, in  \Cref{evaluation} we evaluate the approach on a paradigmatic AC case study.
%
Finally, in \Cref{conclusion} we discuss the results and the path towards deeper AC-RL integration.
